manuscript

### 2023-11-19 scripts/manuscript.qmd
Calculated subscale and total scores, cleaned names, pivoted into tidy format.

```{r}
#| include: FALSE
library(tidyverse)
library(here)
library(rio)
library(psych)
```

```{r}
#| echo: FALSE
communication <- import(here("data", "communication"))
```

# Introduction

>>>>

```{r}
#| include: FALSE
library(tidyverse)
library(here)
library(rio)
library(psych)
library(janitor)
```

```{r}
#| echo: FALSE
communication <- import(here("data", "communication.csv"))
communication <- (clean_names(communication))
```

```{r}
#| echo: FALSE

#creating the new variables: the ppis subscale 1/parental invasive behaviors score, the ppis subscale 2/student defensive behaviors score, and the suspicion scale score
comm <- communication %>%
  mutate(ppis_1_score = rowSums(communication[,5:7])) %>%
  mutate(ppis_2_score = rowSums(communication[,8:15])) %>%
  mutate(ss_score = rowSums(communication[,16:27]))

comm <- comm %>%
  mutate(ppis_total = ppis_1_score + ppis_2_score)
```

```{r}
#| echo: FALSE

#pivoting the data, also removing unnecessary columns
communication <- pivot_longer(comm,
                      cols = ppis_1_1:ss_12,
                      names_to = "item",
                      values_to = "score")

communication <- select(communication, -c(2:7))
```

```{r}
#for ben to do later: create summarize data frames to create into a table
```
# Introduction
